%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  %---------------------------------------------------------
  \cventry
  {Full-stack dApp developer} % Job title
  {Custom Token Bridge} % Organization
  {} % Location
  {Jun. 2025 - present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Ethereum -> Solana custom token bridge using Wormhole}
      \item {Wrote the Ethereum contract for locking tokens and emitting a Wormhole message}
      \item {Wrote backend for relaying Wormhole VAAs to Solana (Wormhole Core Contract)}
      \item {Wrote Solana contract for deserializing posted VAA bytes on Solana and register a vesting schedule if everything checks out}
      \item {Backend: Typescript, Frontend: React}
    \end{cvitems}
  }
  
  %---------------------------------------------------------
  \cventry
  {Solana smart contract developer | Full stack} % Job title
  {CSOV - Trustless Bridge} % Organization
  {} % Location
  {Jan. 2025 - Jun. 2025} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Implemented a trustless lock-and-mint bridge between Substrate (Polkadot) Solochains and Solana}
      \item {Designed the system to be completely trustless: the Solana side trusts only cryptographic verifications}
      \item {NodeJs backend for monitoring the source chain and relaying proofs to Solana}
      \item {React frontend with wallet integrations (Metaplex, Solflare, Subwallet) and signing transactions, displaying progress, etc.}
      \item {Biggest challenges: verify Polkadot's native signatures on Solana; Solana's transaction size limitations; Solana's Compute Unit limitations}
      \item {Technologies used: Rust smart contracts, Node.js, ExpressJs, PostgreSQL, Docker, React}
    \end{cvitems}
  }
  
  %---------------------------------------------------------
  \cventry
    {Full-stack dApp developer} % Job title
    {CSIA - NFT gated dApp} % Organization
    {} % Location
    {May. 2024 - Dec. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created an NFT gated dApp leveraging Solana's SPL token standard and Metaplex}
        \item {Wrote custom NFT gating logic and a backend from scratch}
        \item {Dynamically generated NFT metadata (image, description, etc.) on the backend}
        \item {Collaborated with the client in identifying requirements and issues}
        \item {Technologies used: Solana, SPL token standard, Metaplex, Java, React, PostgreSQL, Docker, Docker Compose}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Architect} % Job title
    {csprUSD - Custom Stablecoin} % Organization
    {} % Location
    {Jan. 2024 - Apr. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design and implement in Rust a stablecoin contract on Casper (blockchain).}
        \item {Develop infrastructure (frontend for interacting with the blockchain, off-chain backend, database)}
        \item {Collaborate in identifying requirements and issues.. Keeping in touch with the smart contract auditing firm.}
        \item {Skills acquired: smart contract design and implementation, Rust language, REST API design, Docker.}
        \item {Technologies used: Rust smart contracts, Casper Blockchain, Casper Wallet, Java, PostgreSQL, Docker, Docker Compose, React}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Fullstack Engineer} % Job title
    {Weavechain} % Organization
    {} % Location
    {Mar. 2022 - Oct. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {worked on Weavechain, a distributed system leveraging blockchain technology for data verifiability}
        \item {Worked on the majority of the codebase, from smart contracts, through Java backend to database integration and frontend development.}
        \item {Improved efficiency of the smart contracts used for storing data hashes on-chain.}
        \item {Monitored and measured backend performance. Identified bottlenecks and rewrote code for improved throughpu}
        \item {Skills acquired: Smart contract development in Solidity, Java performance monitoring and improvements, backend - blockchain interactions (ethereum, hyperledger sawtooth), Geth, C\#, cryptography, multi-threaded Java development, frontend development using React}
        \item {Technologies used: Java, Yourkit, blockchains (Ethereum, Hyperledger Sawtooth, Celo, Ganache), databases (Postgres, MongoDB, Apache Cassandra), Websockets, Docker, Kafka, RabbitMQ, React}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Java Software Engineer} % Job title
    {Coherent Solutions} % Organization
    {} % Location
    {Jun. 2021 - Mar. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {work on microservices for supporting call center automation. Maintenance and continuous support for legacy components.}
        \item {Experience: main focus was designing and developing from scratch a Spring Boot application acting as a Workforce Manager (WFM) to be integrated with the rest of the infrastructure.}
        \item {Extras: developed tools for extracting meaningful information from logs for analytics.}
        \item {Technologies used: Spring Boot, Hibernate, Junit, SonarCube, maven, git, Jenkins, Windows OS, OAuth}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Java Software Engineer} % Job title
    {Flow Traders} % Organization
    {} % Location
    {Oct. 2019 - June. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsibilities: develop and design microservices supporting daily trading activities involving coding of systems for receiving market data and placing orders, handling data in a reliable, performant and traceable manner. }
        \item {Skills acquired: writing object-oriented code to high quality standards based on best recommendations and best practices; software analysis and design using design patterns and concurrency patterns; critical thinking and refactoring; scoping and estimation skills; effective communication skills (verbal and written) in team and across the teams;}
        \item {Tech stack: Java, Kafka, gRPC, Junit, SonarCube, maven, git, Bamboo Oracle Database, Linux OS, React}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Java Developer} % Job title
    {Paddy Power Betfair} % Organization
    {} % Location
    {May. 2019 - Oct. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsibilities: develop microservices related to login, user session management, session caching and user authentication for a complex web application; use of continuous integration and deployment approaches; write well designed, testable, efficient code; ensure quality of product, by extensive code reviews; ensure designs and implementation are in compliance with specifications}
        \item {Skills acquired: object oriented analysis and design using design patterns; refactoring; scoping and estimation skills; effective communication skills (verbal and written);}
        \item {Tech stack: Java, Spring, Cougar framework, Kafka, Junit, Tomcat, chef, maven, git, TargetProcess, Jenkins, Oracle Database, MacOS}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {ITIVITI} % Organization
    {} % Location
    {jun. 2018 - apr. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsibilities: design and develop a financial application; continuous contribution in all phases of the development lifecycle; write well designed, testable, efficient code; ensure quality of product, by extensive code reviews; ensure designs and implementation are in compliance with specifications}
        \item {Skills acquired: object oriented analysis and design using design patterns; refactoring; scoping and estimation skills; effective communication skills (verbal and written);}
        \item {Technologies used: Java, Groovy, C\#, Junit, Spock, git, Gerrit, Gradle, Jenkins, JIRA}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {TORA Trading Services} % Organization
    {} % Location
    {Aug. 2016 - Jun. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsibilities: design and develop a financial application; continuous contribution in all phases of the development lifecycle; write well designed, testable, efficient code; ensure designs and implementation are in compliance with specifications}
        \item {Skills acquired: object oriented analysis and design using common design patterns; scoping and estimation skills; effective communication skills (verbal and written); UNIX OS; profiling}
        \item {Technologies used: Java, JUnit, git, Yourkit, Apache ant}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
